---
title: ''
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# aquanes.report

[![Travis-CI Build Status](https://travis-ci.org/KWB-R/aquanes.report.svg?branch=master)](https://travis-ci.org/KWB-R/aquanes.report)
[![lifecycle](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://www.tidyverse.org/lifecycle/#stable)
[![DOI](https://zenodo.org/badge/83431353.svg)](https://zenodo.org/badge/latestdoi/83431353)


Collects, aggregates and visualises operational analytical data from water suppliers (including a standardised reporting document)

# Demo of reporting tool for Haridwar site   

If you are interested in the capabilities of the R reporting tool, just make sure your computer satisfies the [software requirements](articles/A1_installation.html#pre-required-software) and subsequently execute the following lines of code below in R/RStudio. 

```{r eval=FALSE}
if (!require("devtools")) {
  install.packages("devtools", repos = "https://cloud.r-project.org")
}

devtools::install_github("kwb-r/aquanes.report", 
                         dependencies = TRUE)

aquanes.report::run_app()

```

This will launch the R reporting tool in your default webbrowser. The demo is based on real operational and analytical data for the AQUANES site Haridwar for the time period from 2017-03-24 until 2017-07-25. 
